---
title: "Build new SIBEC tables for 2024 data"
author: "William H MacKenzie"
date: "21/05/2025"
format:
  typst:
    toc: false
    toc-depth: 1
    toc-title: Contents
    section-numbering: 1.1.1
    columns: 1
editor: source
execute:
  echo: false
  error: false
  warning: false
  message: false
  fig.width: 6
  fig.height: 4
  fig.align: 'center'
  fig.cap: true
  fig.pos: H
  out.width: '100%'
  dev: pdf
  fig.ext: pdf
  cache: false
  fig.retina: 2
  dpi: 600
  fig.asp: 1.5
  fig.path: "./figures/"
---

# Evaluation of SIBEC values
This script was built to look at the range of site index by site series or other site factors for the SIBEC dataset compiled by Atticus from the original data sets.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#options(tinytex.verbose = TRUE)
require(tidyverse)
#require (ggplot2)
require (assertr)
require(data.table)
require(DBI)
library(purrr)
require(tictoc)
require(tidymodels)
require(vip)
require(randomForest)
library(knitr)
library(stringr)
require(readxl)
```

##Import SIBEC data

compare the sitebec summaries from 2013 and 2024 to see if there are any differences in the data. This will help to understand how the data has changed over time and if there are any trends that can be identified.

```{r SIBEC and BECdb data import}
require(DBI) #loads odbc as well
 becdb <- dbConnect(odbc::odbc(), .connection_string = "Driver={Microsoft Access Driver (*.mdb, *.accdb)}; DBQ=D:/OneDrive - Government of BC/BECdb_Working/BECdb_ver13_2024.accdb;")
BGC_all <- dbReadTable(becdb, "tblBGC_UnitsWorkingandArchive") %>% 
  filter(is.na(VersionRetired)) %>% select(FSRegion,BGC_Label, BGC_NoSpace, BGC_Zone, Corr1BGC_1) %>% 
  mutate(BGC_Label = trimws(BGC_Label))
SS_all <- dbReadTable(becdb, "tblBEC_SiteSeriesWorkingandArchive") %>% 
  filter(Status == "Current", Forest_NonForest %in% c("Forest", "Treed")) %>%
  select(BGC_NoSpace, SS_NoSpace, SS_Label, SiteSeriesLongName)
SS_new <- dbReadTable(becdb, "tblBEC_SiteSeries_v13_compiled") %>%
  filter(Forest_NonForest %in% c("Forest", "Treed")) %>%
  select(BGC_NoSpace, SS_NoSpace, SS_Label,SiteSeriesLongName)
SS_all <- bind_rows(SS_all, SS_new) %>% distinct() 
dbDisconnect(becdb)
BGCs_noSS <- anti_join(BGC_all , SS_all)

sibec_master <- dbConnect(odbc::odbc(), .connection_string = "Driver={Microsoft Access Driver (*.mdb, *.accdb)}; DBQ=D:/OneDrive - Government of BC/SIBEC_files/SIBEC_2025_VPRO_cleaned.accdb;")
sibec  <- dbReadTable(sibec_master, "SIBEC_All_2025_ENV")
sibec.tree  <- dbReadTable(sibec_master, "SIBEC_All_2025_Trees")
sibec.info  <- dbReadTable(sibec_master, "newSS_from_edatopic")
dbDisconnect(sibec_master)
sibec.info <- sibec.info %>% select(PlotNumber, BGC_spatial, NewSS)
sibec.tree <- sibec.tree %>% select(PlotNumber, TreeSpp, SI50)

sibec25 <- left_join(sibec.tree, sibec.info)
BGC.update <- BGC_all %>% select(BGC_NoSpace, Corr1BGC_1) %>%
  filter(!is.na(Corr1BGC_1)) 
sibec13 <- readxl::read_xlsx("./inputs/sibec2013approx_final.xlsx") %>%
  mutate(BECSiteUnit = paste0(BGCUnit, "/", SiteSeries)) %>%
  select(-Region) %>% distinct %>%
  rename(SiteSeriesLongName = SiteAssociation) %>%
  left_join(BGC.update, by = c("BGCUnit" = "Corr1BGC_1")) %>% 
  mutate(BGC_NoSpace = ifelse(is.na(BGC_NoSpace), BGCUnit, BGC_NoSpace)) %>% 
  select(BGC_NoSpace, BECSiteUnit, SiteSeriesLongName, TreeSpp, MeanPlotSiteIndex, PlotCountSpp)


sibec13$TreeSpp <- sibec13$TreeSpp %>% recode(
  "Sw" = "Sx", "Se" = "Sx", "Acb" = "Ac", "Act" = "Ac") 

```
Summarize SI by site series
```{r}
sibec25.2 <- sibec25 #%>%
  #mutate(BECSiteUnit = str_remove(BECSiteUnit, "[a-z]+$"))%>% #Removes phase designation
  #mutate(BECSiteUnit = str_remove(NewSS, "\\$.*")) %>% #removes seral designation
  #mutate(BGC_NoSpace = str_extract(BECSiteUnit, "^[^/]+")) #extracts BGC from BECSiteUnit
sibec25.sum <- sibec25.2 %>% group_by(NewSS, TreeSpp) %>%
  mutate(meanSI_2025 = mean(SI50, na.rm = TRUE), n_2025 = n(), SE_2025 = sd(SI50, na.rm = TRUE) / sqrt(n_2025)) %>%
  ungroup() %>%
  mutate(NewSS = as.factor(NewSS), TreeSpp = as.factor(TreeSpp)) %>%
  select(-PlotNumber, -SI50) %>% select(BGC_spatial, NewSS, everything()) %>% 
  distinct %>% arrange(NewSS, TreeSpp) %>% filter(n_2025 >= 7)
sibec25.bgc <- sibec25.2 %>% group_by(BGC_spatial, TreeSpp) %>%
  summarise(n_2025 = n()) %>%
  ungroup()

```
Updated SIBEC summary
```{r}
sibec25.ss <- full_join(sibec25.sum, sibec13, by = c("BGC_NoSpace", "TreeSpp")) %>% 
  mutate(across(c(n_2025, PlotCountSpp), ~replace_na(.x, 0))) %>% 
  mutate(SI_diff = meanSI_2025 - MeanPlotSiteIndex, nplots_diff = n_2025 - PlotCountSpp) %>% 
  mutate(PlotCountSpp = as.integer(PlotCountSpp), nplots_diff = as.integer(nplots_diff)) %>% 
 mutate(across(where(is.numeric), round, 2))
 library(openxlsx)
write.xlsx(sibec25.ss, "./outputs/SIBEC_2025_2013_Summary.xlsx", overwrite = TRUE)
## number of samples per BGC to check numbers
## probably need to align old to new BGCs
sibec13.bgc <- sibec13 %>% group_by(BGC_NoSpace, TreeSpp) %>%
  summarise(n_2013 = sum(PlotCountSpp, na.rm = TRUE)) %>%
  ungroup() 
sibec25.bgc <- full_join(sibec25.bgc, sibec13.bgc, by = c("BGC_NoSpace"= "BGC_NoSpace", "TreeSpp")) %>% mutate(across(where(is.numeric), ~replace_na(.x, 0))) %>% mutate(nplot_diff = n_2025-n_2013)
```
## Merge with modelled SIBEC values
```{r}
# pred_SI_SS <- fread("./data/predicted_SI_by_SS.csv")
# sibec25.ss.2 <- left_join(sibec25.ss, pred_SI_SS, by = c("BECSiteUnit" = "SS_NoSpace", "TreeSpp")) %>%
#   mutate(SI25_pred_diff = meanSI_2025 - pred_mean_SI50, SI13_pred_diff = MeanPlotSiteIndex - pred_mean_SI50) %>%
#   mutate(across(where(is.numeric), round, 2))
# fwrite(sibec25.ss.2, "./outputs/SIBEC_2025_2013_Summary_with_predicted.csv", row.names = FALSE)
```

