---
title: "Climatic Optimum SI"
author: "Will MacKenzie"
date: "10/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(plyr)
require(tidyverse)
require(dplyr)
require(forcats)
```

This code is designed to create a prior model of site index for the climatic maximum SI for tree species based on 
1. A Gompertz curve for max SI by DD5
Enter Maximum SI for the species (y axis)
Displacement is the X-axis displacment (not clear what this actually does)
max growth rate = y-axis increment at max rate of change
DD5 is the range of DD5 to model

beginning at the DD5 at which tree growth begins to maximum SI for the species at the DD5 of the BGC which first expresses SImax
2. The maximum curve then decline by an exponential function.

Inputs are a table with min DD5, max SI, DD5 of maximum 

```{r build theoretical SI}
 gompertz <- function(DD5_range, maxSI, maxrate, minDD5){
  y <- maxSI*exp(-exp(maxrate*exp(1)/maxSI*(minDD5- DD5_range)+1))
  return(data.frame(DD5_range =DD5_range, y=y))
}
Gomp_para <- fread("./inputs/GompertzParametersbySpp.csv")

### each species gets a function that dictates SI by DD5.
### the climatic maximum SI for a BGC is calculated from its y value at DD5
spp <- "Fdi"
Gomp_para1 <- Gomp_para %>% filter(Spp %in% spp) 
x <- as.numeric(Gomp_para1[1,c(2:5)])
spp_CSI1 <- gompertz(1:x[1],x[2],x[3],x[4]) %>% dplyr::rename(gomp1 = y) %>% round(1)## estimate for subalpine fir
plot(spp_CSI1)
#gompertz distribution by species
    #need to calculate the max rate based on the DD5 at which maxSI is first achieved.
### reduction in effective DD5 due to high temperatures sets the SI back along the curve 
Gomp_para1 <- Gomp_para %>% filter(Spp %in% spp) 
x <- as.numeric(Gomp_para1[1,c(2:3,6:7)])

spp_CSI2 <- gompertz(1:x[1],x[2],x[3],x[4])%>% dplyr::rename(gomp2 = y) %>% round(1) 
plot(spp_CSI2)
spp_CSI2 <- spp_CSI2 %>% dplyr::select(-DD5_range)

spp_CSI <- bind_cols (spp_CSI1, spp_CSI2) %>%  mutate (CSI = gomp1 - gomp2) %>% dplyr::select(DD5_range, CSI)
spp_CSI$DD5_range <- as.character(spp_CSI$DD5_range)
plot(spp_CSI)


```

```{r compare to BGC data}
allDat <- fread("D:/CommonTables/Climate_Data/ALLWNAv11_AllVars.csv", data.table = FALSE, stringsAsFactors = FALSE) ###Climate data 1961-90for representative points per BGC  with all variables
allDat <- allDat[!(allDat$DD5 == -9999),] %>% mutate_if(is.integer, as.numeric)
allDat$BGC <- as.factor(allDat$BGC)

coastDat <- allDat %>% dplyr::filter(str_detect(BGC, ("CWH|CDF|CMX|MH|MHRF|CVG|CRF|CMA|CWF|CCH")))#, "CMX", "MH", "MHRF", "CVG", "CRF")))
interDat <- allDat %>% dplyr::filter(!str_detect(BGC, ("CWH|CDF|CMX|MH|MHRF|CVG|CRF|CMA|CWF|CCH"))) %>% dplyr::filter(!(BGC== "MSSD")) %>% 
  dplyr::select(BGC, DD5, DD_0) %>% droplevels()
#, "CMX", "MH", "MHRF", "CVG", "CRF")))

BGC_DD5 <- setDT(interDat)[ , .(mean_DD5 = mean(DD5)), by = BGC] 
BGC_DD0 <- setDT(interDat)[ , .(mean_DD0 = mean(DD_0)), by = BGC] %>%  mutate(mean_DD0 = (mean_DD0 - 1000)/5)
BGC_DD0$mean_DD0 <- ifelse(BGC_DD0$mean_DD0 <0, 0, BGC_DD0$mean_DD0) ## reduce DD5 as a function of cold soils
BGC_DD5 <- left_join(BGC_DD5,BGC_DD0 ) %>% mutate(mean_DD5 = mean_DD5 - mean_DD0)
BGC_DD5$mean_DD5 <- BGC_DD5$mean_DD5 %>% round_any(10) %>% as.character()


BGC_SI <- left_join(BGC_DD5, spp_CSI, by = c("mean_DD5" = "DD5_range")) %>% distinct() %>% dplyr::select(-mean_DD5) %>% mutate_if(is.character, as.numeric) %>% arrange(CSI) %>% droplevels() %>%  mutate(BGC= fct_reorder(BGC, CSI)) %>% mutate(SIcat = "" ) %>% if_na(0)
###SI thresholds
x <- as.numeric(Gomp_para1[1,c(8:12)])

BGC_SI$SIcat  <- ifelse(BGC_SI$CSI<=x[1], "0nil",
                        ifelse(BGC_SI$CSI>x[1] & BGC_SI$CSI<=x[2], "1vlow",
                               ifelse(BGC_SI$CSI>x[2] & BGC_SI$CSI<=x[3], "2low",
                                      ifelse(BGC_SI$CSI>x[3] & BGC_SI$CSI<=x[4], "3med",
                                             ifelse(BGC_SI$CSI>x[4] & BGC_SI$CSI<=x[5], "4hi", 
                                                    ifelse(BGC_SI$CSI>x[5], "5max","other")))))) 
ggplot(BGC_SI, aes(BGC,CSI))+
  geom_point()+ 
  theme(axis.text.x = element_text(angle = 90, size = 7) )+
  facet_wrap(.~ SIcat, scales='free', shrink = FALSE, ncol = 2)

```



```{r fit gompertz}
fit.gompertz <- function(data, time){
  d <- data.frame(y=data, t=time)
  
  # Must have at least 3 datapoints at different times
  if (length(unique(d$t)) < 3) stop("too few data points to fit curve")
  
  # Pick starting values ###
  i <- which.max(diff(d$y))
  starting.values <- c(a=max(d$y), 
                       mu=max(diff(d$y))/(d[i+1,"t"]-d[i, "t"]), 
                       lambda=i)
  print("Starting Values for Optimization: ")
  print(starting.values)
  ##########################
  
  formula.gompertz <- "y~a*exp(-exp(mu*exp(1)/a*(lambda-t)+1))"
  nls(formula.gompertz, d, starting.values)
} 
SI <- c(0, 0.1, 5, 9.9, 10)
DD5 <- c(10, 100, 250, 500, 1000)
d <- cbind(DD5, SI)
d <- as.data.frame(d)
fit <- fit.gompertz(d$SI, d$DD5)

plot(d)
lines(d$DD5, predict(fit))

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
##Here is an example of the R-code I used to fit Gompertz model to my data (number of cases of Ebola in Liberia):
################################### ### GOMPERTZ
alpha = 9526 beta = 9.1618 k = 0.0028
nls.gompertz <- minpack.lm::nlsLM(data$cases ˜ alpha*exp(-beta*exp(-k*data$days)), data = data, start = list(alpha = alpha, beta = beta, k = k), control = list(maxiter = 500))
coef(nls.gompertz) ## alpha = 9437, beta = 59.24, k = 0.0219
## Now fit Geompertz model
growth.gompertz <- growthmodels::gompertz(data$days, alpha = coef(nls.gompertz)[["alpha"]], beta = coef(nls.gompertz)[["beta"]], k = coef(nls.gompertz)[["k"]])
growth.gompertz
## Predict
predict.gompertz <-growthmodels::gompertz(days.predict, alpha = coef(nls.gompertz)[["alpha"]], beta = coef(nls.gompertz)[["beta"]], k = coef(nls.gompertz)[["k"]])
predict.gompertz
## the values for 18/4, 18/5, 18/6, and 18/7 predict.gompertz[c(84:87)]
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
