---
title: "Prepare edaphic sites for estimating SI50"
author: "William H MacKenzie"
date: "29/11/2019"
output:
  pdf_document: default
  html_document: default
---
This script selects a number of sites per BGC and creates 40 records one for each edatopic position.
Will need to move the attribution of predictors to points to a separate script in line with the model building script.
This data set will be then be predicted by the SIBEC model and used to create estimates of SI50 for each edatopic position and site series within BGCs

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tinytex.verbose = TRUE)
require(tidyverse)
require (ggplot2)
require(data.table)
# require(DBI)
# library(purrr)
# require(SIndexR)
require(sf)
require(terra)
```

##Import Vtrees data

Create BGC point data and build predictor data
need site_id, BGC, lat, long, elev
```{r build grid and add elevation}
BC.climr <- fread("../aSMR_X_rSMR/inputs/WNA_BGC_climr.csv") %>%
  filter(!is.na(CMD)) %>%  # Remove NA values in CMD
  filter(PERIOD == "1961_1990")# %>%  # Keep only relevant period
  #filter(!str_detect(BGC, "_"))  # Remove any BGC strings containing "_"
## sample 10 sites from each BGC and filter out those with < 10 sites
BC.climr2 <- BC.climr %>%
  group_by(BGC) %>%
  group_map(~slice_sample(.x, n = min(10, nrow(.x))), .keep = TRUE) %>%
  bind_rows()

## for each site create a list of records for 5 levels of SNR and 8 levels of rSMR
SNR = c("A", "B", "C", "D", "E")
rSMR = c(0, 1, 2, 3, 4, 5, 6, 7)
new_records <- expand.grid(SNR = SNR, rSMR = rSMR)
BC.climr <- crossing(BC.climr2, new_records) #%>% filter(BGC == "SBSmc2")

sPPTtemp <- BC.climr %>% select("id", "PPT_05","PPT_06","PPT_07","PPT_08","PPT_09" )
BC.climr$Moist <- rowSums(sPPTtemp[,2:6] >90)
BC.climr <- BC.climr %>% mutate(CMD = ifelse(Moist >4, CMD * 0.75, CMD))

#temp2 <- temp2[temp2$Moist != "",] # only those points calculated to be moist
#####################################
#sibec.anal2 <- sibec.anal2[,c("id","PPT_at","PPT_wt","PAS", "CMD", "DD5")]
#allDat2 <- cbind(wPPTtemp,CMDtemp)
#allDat <- cbind(wPPTtemp,sPPTtemp[c("Moist")])
#allDat <- cbind(allDat,temp,temp2) ### use this one if Moist indicator is completed above
BC.climr$PPT.dorm <- BC.climr$PPT_at + BC.climr$PPT_wt
BC.climr$Def <- 350 - BC.climr$PPT.dorm 
BC.climr$Def[BC.climr$Def < 0] <- 0 #negative values set to zero = no deficit
BC.climr$CMD <- BC.climr$CMD + BC.climr$Def
BC.climr2 <- BC.climr %>% mutate(CMD.adj = ifelse(rSMR == 3, CMD + 125, 
                                                  ifelse(rSMR == 2, CMD + 250,
                                                         ifelse(rSMR == 1, CMD + 375,
                                                                ifelse(rSMR == 0, CMD + 500,
                                                                       ifelse(rSMR == 5, CMD/2,
                                                                              ifelse(rSMR == 6, CMD/4,
                                                                                     ifelse(rSMR == 7, CMD/8,
                                                                                            ifelse(rSMR == 4, CMD, NA)))))))))%>% 
  mutate(CMD.adj = ifelse(CMD.adj < 0, 0, CMD.adj))

# Read the rules table
rules_table <- fread("../aSMR_X_rSMR/inputs/aSMR_Rules_HalfStep_v13_7May2025.csv")
labels <- fread("../aSMR_X_rSMR/inputs/aSMR_labels.csv")

# Ensure column names are consistent
colnames(rules_table) <- c("SMRLevel", "CMD.range", "aSMR")
#sibec.anal.test <- sibec.anal2 %>% filter(PlotNumber == "0002801") %>% filter(TreeSpp == "Ss")
# Merge with sibec.anal based on the rSMR field
BC.climr3 <- BC.climr2 %>% 
  left_join(rules_table, by = c("rSMR" = "SMRLevel")) %>%  filter(CMD.range <= CMD.adj) %>%  group_by(id, rSMR) %>% slice_max(CMD.range) %>% ungroup() %>% 
  select(-CMD, -CMD.range) %>% data.frame %>% left_join(labels, by = c("aSMR" = "aSMR")) 
# BC.climr <- BC.climr %>% mutate(eda2 = paste0(aSMR_label, '/', rSNRg))
BC.climr3 <- BC.climr3 %>% select(id, BGC, Latitude = lat, DD5, rSMR, aSMR, SNR, CMD.adj, PAS, CMI, bFFP, DD18, Eref)
fwrite(BC.climr3, "./data/Edaphic_sites_data_2025.csv")

```
```{r potenial solar radiation}
# Load required package
# library(meteoland)
# 
# # Example dataset with point locations
# points <- data.frame(
#   SiteID = c("A", "B", "C", "D", "E"),
#   Latitude = c(48.5, 50.2, 51.8, 53.1, 54.7),  # Degrees North
#   Longitude = c(-123.5, -124.2, -125.0, -126.1, -127.3),  # Degrees West
#   Slope = c(5, 20, 35, 15, 25),  # Slope in degrees
#   Aspect = c(90, 180, 225, 270, 360)  # Aspect in degrees (east of north)
# )
# 
# xx <- meteoland::radiation_potentialRadiation(solarConstant = 1367, latrad = 48.5, slorad = -124, asprad = 90, delta = NULL)
# # Apply potential radiation function
# points <- points %>%
#   mutate(PotentialRadiation = mapply(meteoland::radiation_potentialRadiation, Latitude, Slope, Aspect))
# 
# # View dataset with computed radiation values
# print(points)
```

