---
title: "SIBEC_Evaluation"
author: "William H MacKenzie"
date: "29/11/2019"
output:
  pdf_document: default
  html_document: default
---
# Evaluation of SIBEC values
This script was built to look at the range of site index by site series or other site factors for the SIBEC dataset compiled by Atticus from the original data sets.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tinytex.verbose = TRUE)
require(plyr)
require(dplyr)
require(tidyr)
require(TeachingDemos)
require (ggplot2)
require (assertr)
require(data.table)
require(tinytex)
```

##Import Vtrees data

Read in SIBEC data from a .csv table export of a _Trees table from the VTrees database

```{r Vtrees data import}
#SI_raw <- fread("./SI_Prediction/SIBEC_SBSmc2_2019_Trees.csv") ##v1 recalcuated SI using Count Age and TotalHtCalc
SI_raw <- fread("./SI_Prediction/SBS_mc2_Trees_new.csv") ##v2 Use the AgeBH where available - gets rid of some outliers. Sx starts looking better 
#SI_explore <- fread("SBSmc2_SI_Cleaned.csv")
table(SI_raw[,SiteSeries])
sort(unique(SI_raw$TreeSpp))# examine unique tree codes for harmonization
SI_raw <- as.data.frame(SI_raw)
##### Clean up Species Codes
SI_raw$TreeSpp <- SI_raw$TreeSpp %>% recode(
  "Sw" = "Sx", "sw" = "Sx", "Se" = "Sx",
  "EP"= "Ep", "FD" = "Fd", "Fd " = "Fd", "PL" = "Pl")

SI_raw$NutrientRegime <- toupper(SI_raw$NutrientRegime)
SI_raw <- SI_raw[!SI_raw$TreeSpp == "",]
sort(unique(SI_raw$TreeSpp)) # check for any other miscodes
SI_info <- SI_raw %>% select(Zone, SubZone, SiteSeries, TreeNum, MoistureRegime, NutrientRegime)
### Reduce the variable set for submission to Site Tools
SI_clean <-  SI_raw %>% select(PlotNumber,TreeSpp, NewAge, TotalHtCalc) %>% dplyr::rename(Species = TreeSpp, `BHAge` = NewAge, `Height` = TotalHtCalc )
write.csv(SI_clean, "./SI_Prediction/SIBEC_SBScm2_2019_ForSiteTools_v2.csv", row.names = FALSE) ####submit this file to Site Tools (no file header)
```

## Merge SiteTools site index estimations with Site data
CSV files submitted to SiteTools 4.1 are read in and merged with plot information.

SiteTools curves can be run for either interior or coastal locations. Run both algorithms on the same datasets in SiteTools and merge together the results from the two files if the data set includes collections from both regions
```{r tidy SIBEC data, echo=TRUE}
###merge the results back into the dataframe
SI_clean_interior <- fread("./SI_Prediction/SIBEC_SBSmc2_2019_SiteTools4.1_interior_v2.csv")
SI_clean_interior <- cbind(SI_info, SI_clean_interior)
SI_tidy <- SI_clean_interior
#------------Include if data needs both interior and coastal SI for complete set of tables
# SI_clean_coast <- fread("./SI_Prediction/SIBEC_All_2019_SiteTools4.1_coast.csv")
# SI_clean_coast <-  SI_clean_coast %>% select('Site Index m') %>% dplyr::rename(SI_coast = 'Site Index m')
# SI_tidy <- cbind(SI_clean_interior, SI_clean_coast)

SI_tidy <- SI_tidy[!duplicated(SI_tidy),]
SI_tidy <- SI_tidy %>% dplyr::rename(BHAge = 'BH Age yrs', Height = 'Height m', SI_interior = 'Site Index m')
#SI_tidy <- SI_tidy[complete.cases(SI_tidy)]
SI_tidy <- SI_tidy[! (SI_tidy$SiteSeries == ""),]
SI_tidy$edatope <-  paste0(SI_tidy$MoistureRegime , SI_tidy$NutrientRegime)
SI_tidy$edatope2 <-  paste0(SI_tidy$NutrientRegime,SI_tidy$MoistureRegime)
write.csv(SI_tidy, "./SI_Prediction/SIBEC_SBSmc2_2019_v2.csv", row.names = FALSE)
```

## Generate boxplots of site index by site series with phases
This produces a facetted boxplot graph for each species in a BGC showing site index by site series

```{r boxplot SS phases graphs raw, fig.width = 12, fig.height = 8, fig.cap = "Fig. 0 Site Index by Site Series with phases all data for each species in the SBSmc2" }
table(SI_tidy[, "SiteSeries"])
SI_spp <- SI_tidy %>% filter(Zone == "SBS", SubZone == "mc2")#, Species == "Lw")
SI_spp <- drop_na (SI_spp)
SI_sppsave <- SI_spp
table(SI_spp[, "SiteSeries"])

SI_spp$SiteSeries <- as.factor(SI_spp$SiteSeries)

#sets order for site series -- need to make this more universal
SI_spp$SiteSeries <- factor(SI_spp$SiteSeries, levels = c("02", "03", "01c", "01b", "01a", "01",#
                                                          "04", "05", "06", "09b","09", "09a", #
                                                           "10a","10", "07","10b","12"))# "12a",
#-------Produce boxplot
BGC = "SBSmc2"
SI_box <- ggplot(SI_spp, aes(x=SiteSeries, y=SI_interior, fill=Species)) + 
  geom_boxplot()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))+
  ggtitle(paste0 ("Site Index by Site Series phases for the "), BGC)+
  facet_wrap(~Species)
plot(SI_box)

ggsave("SIxSSphaseraw_boxplot_SBSmc2ver2.jpg", SI_box, device="jpeg", path = "./SI_prediction/outputs/")

```

```{r boxplot SS phases graphs, fig.width = 12, fig.height = 8, fig.cap = "Fig. 1 Site Index by Site Series with phases - removed some outliers for each species in the SBSmc2" }

remove <-c("SBC3727", "SBC3724", "SBC3711", "SBC3712", "SBC3686", "SBC7318", "SBC3109", "SBC3108","SBC3422",
            "SBC6092", "SBC3716", "SBC3714", "SBC6145" ) # these are 12 plots with much higher productivity than the second set (2 phases?)
SI_spp1 <- SI_spp [!(SI_spp$PlotNumber %in% remove), ]
table(SI_spp1[, "SiteSeries"])

SI_spp1$SiteSeries <- as.factor(SI_spp1$SiteSeries)

##box blot of site index by site series for selected zone
#sets order for site series -- need to make this more universal
SI_spp1$SiteSeries <- factor(SI_spp1$SiteSeries, levels = c("02", "03", "01c", "01b", "01a", "01",#
                                                          "04", "05", "06", "09b","09", "09a", #
                                                           "10a","10", "07","10b","12"))# "12a",
#-------Produce boxplot
BGC = "SBSmc2"
SI_box1 <- ggplot(SI_spp1, aes(x=SiteSeries, y=SI_interior, fill=Species)) + 
  geom_boxplot()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))+
  ggtitle(paste0 ("Site Index by Site Series phases for the "), BGC)+
  facet_wrap(~Species)
plot(SI_box1)

ggsave("SIxSSphase2_boxplot_SBSmc2ver2.jpg", SI_box1, device="jpeg", path = "./SI_prediction/outputs/")

```

## Generate boxplots of site index by site series without phases
This produces a facetted boxplot graph for each species in a BGC showing site index by site series

```{r boxplot SS graphs, fig.width = 12, fig.height = 8, fig.cap = "Fig. 2 Site Index by Site Series (no phases) for each species in the SBSmc2" }
### remove any phase designations
SI_spp1$SiteSeries <- as.character(SI_spp1$SiteSeries)
SI_spp2 <- SI_spp1 %>% 
      mutate(SiteSeries_rename = ifelse(SiteSeries %in% c('01a', '01b', '01c'), '01', 
                     ifelse(SiteSeries %in% c('09a', '09b'), '09',
                            ifelse (SiteSeries %in% c('10a','10b'), '10', SiteSeries))))
table(SI_spp2[, "SiteSeries_rename"])

#SI_spp2$SiteSeries_rename <- as.factor(SI_spp2$SiteSeries_rename)

##box blot of site index by site series for selected zone
#sets order for site series -- need to make this more universal
SI_spp2$SiteSeries_rename <- factor(SI_spp2$SiteSeries_rename, levels = c("02", "03",  "01",#"01c", "01b", "01a",
                                                          "04", "05", "06", "09", #"09b", "09a",
                                                           "10", "07","12"))#"10a","10b", "12a",
#-------Produce boxplot
BGC = "SBSmc2"
SI_box2 <- ggplot(SI_spp2, aes(x=SiteSeries_rename, y=SI_interior, fill=Species)) + 
  geom_boxplot()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))+
  ggtitle(paste0 ("Site Index by Site Series (no phases) for the "), BGC)+
  facet_wrap(~Species)
plot(SI_box2)

ggsave("SIxSS_boxplot_SBSmc2ver2.jpg", SI_box2, device="jpeg", path = "./SI_prediction/outputs/")



```


## Generate boxplots of site index by soil moisture regime
This produces a facetted boxplot graph for each species in a BGC showing site index by site series

```{r boxplot SMR graphs, fig.width = 12, fig.height = 8, fig.cap = "Fig. 3 Site Index by SoilMoisture Regime for each species in the SBSmc2" }
#-------Produce boxplot
table(SI_spp[, "MoistureRegime"])
SI_spp$MoistureRegime <- as.factor(SI_spp$MoistureRegime)
SI_box3 <- ggplot(SI_spp, aes(x=MoistureRegime, y=SI_interior, fill=Species)) + 
  geom_boxplot()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))+
  ggtitle(paste0 ("Site Index by SMR for the "), BGC)+
  facet_wrap(~Species)
plot(SI_box3)

ggsave("SIxEdatopeSMR_boxplot_SBSmc2ver2.jpg", SI_box3, device="jpeg", path = "./SI_prediction/outputs/")


```
## Generate Plots by Edatope organized by SMR groups

```{r boxplot edatopicxSMR graphs, fig.width = 12, fig.height = 8, fig.cap = "Fig. 4 Site Index by Edatope-SMR for each species in the SBSmc2" }
#-------Produce boxplot
table(SI_spp[, "edatope"])
SI_spp$edatope <- as.factor(SI_spp$edatope)
SI_box4 <- ggplot(SI_spp, aes(x=edatope, y=SI_interior, fill=Species)) + 
  geom_boxplot()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))+
  ggtitle(paste0 ("Site Index by Edatope for the "), BGC)+
  facet_wrap(~Species)
plot(SI_box4)

ggsave("SIxEdatopeSMR_boxplot_SBSmc2ver2.jpg", SI_box4, device="jpeg", path = "./SI_prediction/outputs/")


```

## Generate Plots by Edatope organized by SNR groups
```{r boxplot edatopicxSNR graphs, fig.width = 12, fig.height = 8, fig.cap = "Fig. 5 Site Index by Edatope-SNR for each species in the SBSmc2" }
#-------Produce boxplot
table(SI_tidy[, "edatope2"])
SI_box5 <- ggplot(SI_spp, aes(x=edatope2, y=SI_interior, fill=Species)) + 
  geom_boxplot()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))+
  ggtitle(paste0 ("Site Index by Edatope for the "), BGC)+
  facet_wrap(~Species)
plot(SI_box5)

ggsave("SIxEdatopeSNR_boxplot_SBSmc2ver2.jpg", SI_box5, device="jpeg", path = "./SI_prediction/outputs/")

```

