---
title: "SIBEC Regressions"
author: "Will MacKenzie/Kiri Daust"
date: "17/06/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
require(dplyr)
require(ggplot2)
require(magrittr)
require(foreach)
require(reshape2)
require(reticulate)
require(Rcpp)
library(data.table)
library(scales)
require(rgdal)
require(tidyverse)
require(randomForest)
require(Rcpp)
require(openxlsx)

calcCMD <- function(CMD, rSMR){
  diff <- rSMR - 4
  if(diff > 0){
    return(CMD/2^diff)
  }else if(diff < 0){
    return(CMD + 100*abs(diff))
  }else{
    return(CMD)
  }
}
calcCMD_vec <- Vectorize(calcCMD)

cppFunction('NumericVector calcASMR(NumericVector rSMR,NumericVector CMD, DataFrame Rules) {
  NumericVector rSMRLev = Rules["SMRLevel"];
  NumericVector CMDctf = Rules["CMD"];
  NumericVector aSMR = Rules["aSMR"];
  int len = CMD.length();
  IntegerVector v;
  NumericVector out(len);
  for(int i = 0; i < len; i++){
    v = Rcpp::seq(0, aSMR.length()-1);
    if(rSMR[i] < 5){
      v = v[rSMRLev == 0];
    }else if(rSMR[i] == 5){
      v = v[rSMRLev == 5];
    }else if(rSMR[i] == 6){
      v = v[rSMRLev == 6];
    }else{
      v = v[rSMRLev == 7];
    }
    int j;
    for(j = v[0]; j < v[v.length()]; j++){
      if(CMD[i] <= CMDctf[j]){
        break;
      }
    }
    out[i] = aSMR[j];
  }
  return(out);
}')
```

```{r importData}
sibec <- fread("./inputsGit/SIBEC_2020_updatesof2013.csv")
sibec_add <- fread("./inputsGit/SIBEC_2020_Add.csv") ## additional SI Max values added
sibec_add <- sibec_add %>% dplyr::select(-Source)
sibec <- rbind(sibec, sibec_add)
sibec <- sibec[!is.na(MeanPlotSiteIndex),]
MaxSppSI <-  fread("./inputsGit/MaxSppSI.csv") ## file with highest know SI values by species


Spp = "Fd"

SppMaxSI <- MaxSppSI[MaxSppSI$Sp %in% Spp,]
sibec <- sibec[TreeSpp == Spp,]
sibec[,BGC := gsub("/.*","",SS_NoSpace)]

sibec[,isMax := MeanPlotSiteIndex == max(MeanPlotSiteIndex), by = .(BGC)]
simax <- sibec[(isMax),] 
simax <- simax %>% dplyr::rename (XSI = MeanPlotSiteIndex) %>% unique()

##load and average climate data
climDat0 <- fread("C:/Users/kirid/Sync/CCISS_data/CommonTables/WNA_4k_HexPts_BGC_Normal_1961_1990MSY.csv")
#climDat0 <- fread("C:/Users/whmacken/Sync/CCISS_data/CommonTables/WNA_4k_HexPts_BGC_Normal_1961_1990MSY.csv")
climDat <- climDat0[,lapply(.SD, mean), by = .(BGC), .SDcols = 174:252]

##check if max SI values are near max climatic potential

eda <- fread("C:/Users/kirid/Sync/CCISS_data/CommonTables/Edatopic_v11_20.csv")
eda <- eda[is.na(Special),.(BGC,SS_NoSpace,Edatopic)]
eda[,`:=`(rSMR = as.numeric(substr(Edatopic,2,2)),SNR = substr(Edatopic,1,1))]
eda <- unique(eda)

rules <- fread("./inputsGit/aSMR_Rules_HalfStep_v11_09Dec2019.csv")
simax2 <- eda[simax, on = "SS_NoSpace"]
simax2 <- climDat[,.(BGC,CMD)][simax2, on = "BGC"]
simax2 <- simax2[!is.na(CMD),]
simax2[, CMDadj := calcCMD_vec(CMD,rSMR)]
simax2[, aSMR := calcASMR(rSMR,CMDadj,rules)]
simax2[, aSMR := round(aSMR, digits = 0)]

sppAdj <- data.table(read.xlsx("./inputsGit/SI_percent_by_edagrid.xlsx",sheet = "Fd"))
sppAdj$aSMR <- 0:9
sppAdj <- melt(sppAdj, id.vars = "aSMR", variable.name = "SNR")

simax2 <- sppAdj[simax2, on = c("aSMR","SNR")]
simaxAvg <- simax2[,.(BGC,XSI,PropMax = mean(value)), by = .(SS_NoSpace)]
simaxAvg <- unique(simaxAvg)

###----will need to remove or adjust the SI where the max is on suboptimal CMD sites (e.g. where species only occurs on warm, dry sites)

##-------Removed for Fd curves
simax <- simax %>% filter(!str_detect(simax$BGC, ("CDFmm|SBPSxc|IDFxm|ESSFmw|IDFdk4|ESSFxw_OR|IDFxh2|IDFdm2|IDFdm1|IDFxw|IDFxh1|IDFdk|SBSmw|SBSdw|ICHmk")))

##-------Removed for Bg curves
#simax <- simax %>% filter(!str_detect(simax$BGC, ("CDFmm|SBPSxc|IDFxm|ESSFmw|IDFdk4|ESSFxw_OR|IDFxh2|IDFdm2|IDFdm1|IDFxw|IDFxh1|IDFdk|SBSmw|SBSdw|ICHmk")))

climSI <- left_join(simax, climDat) %>% dplyr::select(BGC, XSI, DD5, DD18, EXT) #%>% mutate(XSIadj = ifelse (DD5 >= 1100, XSI + ((DD5 - 1100) *.02), XSI))
coastSI <- climSI %>% dplyr::filter(str_detect(BGC, ("CWH|CDF|CMX|MH|MHRF|CVG|CRF|CMA|CWF|CCH|IDFww|ESSFmk")))#, "CMX", "MH", "MHRF", "CVG", "CRF")))
interSI<- climSI %>% dplyr::filter(!str_detect(BGC, ("CWH|CDF|CMX|MH|MHRF|CVG|CRF|CMA|CWF|CCH|IDFww|ESSFmk")))#, "CMX", "MH", "MHRF", "CVG", "CRF")))

clim_coast <- climDat %>% dplyr::filter(str_detect(BGC, ("CWH|CDF|CMX|MH|MHRF|CVG|CRF|CMA|CWF|CCH|IDFww|ESSFmk"))) %>% dplyr::select(BGC, DD5, DD18, EXT) 
clim_inter <- climDat %>% dplyr::filter(!str_detect(BGC, ("CWH|CDF|CMX|MH|MHRF|CVG|CRF|CMA|CWF|CCH|IDFww|ESSFmk"))) %>% dplyr::select(BGC, DD5, DD18, EXT) 

```


``` {r plot}
SImaxc <- SppMaxSI[SppMaxSI$cos_int == "c", ]
pc <- ggplot(coastSI, aes(x = DD5, y = XSI))+
  geom_point() +
  #geom_point(shape = 21, fill = "red", size = 1)+
  geom_jitter(width = 0) +
  scale_y_continuous(limit = c(0, 45))+
     scale_x_continuous(limit = c(0, 5000))+
    ggtitle("DD5 range by Coastal BGC")+
  geom_text (aes(label= BGC), size = 2, hjust = -.1, position = position_dodge(width=1) )+
  #geom_abline(intercept = -11, slope = .042, color = "green")+
  #geom_abline(intercept = -1.86715, slope = .0263, color = "red")+
  geom_hline(yintercept= (SppMaxSI$MaxSI), linetype="dashed", color = "red")+
geom_smooth(method = "loess")
  #geom_smooth(method = "lm")

  #scale_y_continuous("DD5", breaks=seq(0,8000,500))+
  #theme_bw()
  #geom_text (aes(label= BGC), size = 1, hjust = -1, position = position_dodge(width=1) )#
#ggsave("./outputs/CMD_ranges of Expert aSMR of Zonal.pdf", plot = p, dpi = "print", device = "pdf", width = 15, height = 15, units = "cm")
#ggsave("./outputs/CMD_ranges.png", plot = p, dpi = "print", device = "png", width = 15, height = 15, units = "cm")
plot(pc)


interSI2 <- interSI %>% filter(DD5 <=750)
SImaxi <- SppMaxSI[SppMaxSI$cos_int == "i", ]
#interSI2 <- interSI %>% dplyr::filter(!str_detect (BGC, "PPxh1|BGxh2|BGxh1"))
pi <- ggplot(interSI, aes(x = DD5, y = XSI))+
  geom_point() +
  #geom_point(shape = 21, fill = "red", size = 1)+
  geom_jitter(width = 0) +
 # coord_flip()+
    ggtitle("SI by DD5 Interior")+   xlab ("DD5")+
   scale_x_continuous(limit = c(0, 3000))+
  scale_y_continuous(limit = c(0, 45))+
  #geom_segment(aes(x=350, y=0, xend=1100, yend = 28))+
  #geom_abline(intercept = -11, slope = .042, color = "green")+
  #geom_abline(intercept = -1.86715, slope = .0263, color = "red")+
  geom_hline(yintercept = (SImaxi$MaxSI), linetype="dashed", color = "red")+
    geom_text (aes(label= BGC), size = 2, hjust = -.1, position = position_dodge(width=1) )+
geom_smooth(method = "loess")
#geom_smooth(method = "lm")

#+
  #theme_bw()
  #geom_text (aes(label= BGC), size = 4, hjust = -.1, position = position_dodge(width=1) )#
#ggsave("./outputs/CMD_ranges of Expert aSMR of Zonal.pdf", plot = p, dpi = "print", device = "pdf", width = 15, height = 15, units = "cm")
#ggsave("./outputs/CMD_ranges.png", plot = p, dpi = "print", device = "png", width = 15, height = 15, units = "cm")
plot(pi)


```

```{r build loess and extrapolate}
## interior
spp.lo <- loess(XSI ~ DD5, interSI, control = loess.control(surface = "direct"))
#predict(spp.lo, data.frame(DD5 = seq(0, 3000, 100)), se = TRUE)
PredictedSI <- predict(spp.lo, newdata = clim_inter , se = F)
PredictedSI_int <- cbind(clim_inter, PredictedSI)
#write.csv(PredictedSI_int, paste0("./outputs/", Spp, "_interior_SIpotential_predicted.csv"))

## coast
spp.lo2 <- loess(XSI ~ DD5, coastSI, control = loess.control(surface = "direct"))
#predict(spp.lo2, data.frame(DD5 = seq(0, 3000, 100)), se = TRUE)
PredictedSI <- predict(spp.lo2, newdata = clim_coast , se = F)
PredictedSI_coast <- cbind(clim_coast, PredictedSI)
#write.csv(PredictedSI_coast, paste0("./outputs/", Spp, "_coast_SIpotential_predicted.csv"))

```

```{r plot predicted}
#pi <- 
  ggplot(PredictedSI_int, aes(x = DD5, y = PredictedSI))+
  geom_point() +
  #geom_point(shape = 21, fill = "red", size = 1)+
  geom_jitter(width = 0) +
  scale_y_continuous(limit = c(0, 45))+
     scale_x_continuous(limit = c(0, 5000))+
    ggtitle("DD5 range by Coastal BGC")+
  geom_text (aes(label= BGC), size = 2, hjust = -.1, position = position_dodge(width=1) )+
  #geom_abline(intercept = -11, slope = .042, color = "green")+
  #geom_abline(intercept = -1.86715, slope = .0263, color = "red")+
  geom_hline(yintercept= (SppMaxSI$MaxSI), linetype="dashed", color = "red")+
geom_smooth(method = "loess")

ggsave(paste0 ("./outputs/", Spp, "_interior_SIpotential_predicted.jpg"))

#pc <- 
  ggplot(PredictedSI_coast, aes(x = DD5, y = PredictedSI2))+
  geom_point() +
  #geom_point(shape = 21, fill = "red", size = 1)+
  geom_jitter(width = 0) +
  scale_y_continuous(limit = c(0, 45))+
     scale_x_continuous(limit = c(0, 5000))+
    ggtitle("DD5 range by Coastal BGC")+
  geom_text (aes(label= BGC), size = 2, hjust = -.1, position = position_dodge(width=1) )+
  #geom_abline(intercept = -11, slope = .042, color = "green")+
  #geom_abline(intercept = -1.86715, slope = .0263, color = "red")+
  geom_hline(yintercept= (SppMaxSI$MaxSI), linetype="dashed", color = "red")+
geom_smooth(method = "loess")
ggsave(paste0 ("./outputs/", Spp, "_coast_SIpotential_predicted.jpg"))

```

## Adjust by edatopic position

```{r eda_adjust}
predictComb <- as.data.table(rbind(PredictedSI_coast,PredictedSI_int))
predictComb <- predictComb[,.(BGC,PredictedSI)]
temp <- climDat[,.(BGC,CMD)]
predictComb <- temp[predictComb, on = "BGC"]

predictComb <- eda[predictComb, on = "BGC"]
predictComb[, CMDadj := calcCMD_vec(CMD,rSMR)]
predictComb[, aSMR := calcASMR(rSMR,CMDadj,rules)]
predictComb[, aSMR := round(aSMR, digits = 0)]

predictComb <- sppAdj[predictComb, on = c("aSMR","SNR")]
predictComb[,PredictedSI := PredictedSI*value]
predSIfinal <- predictComb[,.(BGC, SS_NoSpace, Edatopic, aSMR, PredictedSI)] ##each edatopic position
SIbySS <- predSIfinal[,.(SIPred = mean(PredictedSI)), by = .(SS_NoSpace)] ##averaged by site series
```


























vars <- names(climDat)[-1]
#suit <- fread("C:/Users/kirid/Sync/CCISS_data/CommonTables/Feasibility_v11_21.csv")
suit <- fread("C:/Users/whmacken/Sync/CCISS_data/CommonTables/Feasibility_v11_21.csv")
suit <- suit[Spp == "Fd",.(BGC,SS_NoSpace,Spp,Feasible)]
suit[,isMax := Feasible == min(Feasible), by = .(BGC)]
suit2 <- suit[(isMax), head(.SD,1), by = .(BGC)]
sibec <- merge(sibec, suit2, by = "BGC", all = T)
#units <- fread("C:/Users/kirid/Sync/CCISS_data/CommonTables/All_BGCs_v11_21.csv")
units <- fread("C:/Users/whmacken/Sync/CCISS_data/CommonTables/All_BGCs_v11_21.csv")
BC.units <- units[DataSet == "BC",Map_Label]
climDat <- climDat[BGC %in% BC.units,]
treeClm <- sibec[climDat, on = "BGC"]

minSI <- treeClm[MeanPlotSiteIndex < quantile(MeanPlotSiteIndex,0.03, na.rm = T),.(BGC,MeanPlotSiteIndex,DD5)]
minVals <- data.table(x = c(mean(minSI$DD5), min(treeClm$DD5)), y = c(mean(minSI$MeanPlotSiteIndex),0))
dd5Fit <- lm(y ~ x, data = minVals)
coefs <- dd5Fit$coefficients
treeClm[is.na(MeanPlotSiteIndex), MeanPlotSiteIndex := coefs[1]+coefs[2]*DD5]
dat <- treeClm[,c("BGC","MeanPlotSiteIndex",..vars)]
dat <- unique(dat)

##now hotter units
#climDat <- fread("C:/Users/kirid/Sync/CCISS_data/CommonTables/WNA_4k_HexPts_BGC_Normal_1961_1990MSY.csv")
climDat <- climDat0[,lapply(.SD, mean), by = .(BGC), .SDcols = 174:252]
#units <- fread("C:/Users/kirid/Sync/CCISS_data/CommonTables/All_BGCs_v11_21.csv")
units <- fread("C:/Users/whmacken/Sync/CCISS_data/CommonTables/All_BGCs_v11_21.csv")
US.units <- units[DataSet == "USA",Map_Label]
climDat <- climDat[BGC %in% US.units,]
suitClm <- suit[climDat, on = "BGC"]
temp <- suitClm[,.(BGC,Feasible,DD5,DD18,DD18_sm,Eref,CMD)]
suit.fit <- step(lm(Feasible ~1, data = temp[!is.na(Feasible)]), 
     scope = list(lower = ~1, upper = ~ DD5*DD18*Eref*CMD), trace = 3)
suitClm[CMD > quantile(CMD,0.95) & DD18 > quantile(DD18, 0.95), MeanPlotSiteIndex := 5]
suitClm <- suitClm[!is.na(MeanPlotSiteIndex),c("BGC","MeanPlotSiteIndex",..vars)]
dat <- rbind(dat, suitClm)

climDat <- suit[climDat, on = "BGC"]
treeClm <- climDat[sibec, on = "BGC"]
treeClm <- treeClm[!is.na(treeClm$DD5),]
datCoast <- treeClm %>% dplyr::filter(str_detect(BGC, ("CWH|CDF|CMX|MH|MHRF|CVG|CRF|CMA|CWF|CCH")))#, "CMX", "MH", "MHRF", "CVG", "CRF")))
datInterior <- treeClm%>% dplyr::filter(!str_detect(BGC, ("CWH|CDF|CMX|MH|MHRF|CVG|CRF|CMA|CWF|CCH")))#, "CMX", "MH", "MHRF", "CVG", "CRF")))
#datCoast <- treeClm[grep("^C.*",BGC),]
#datInterior <- treeClm[!BGC %in% datCoast$BGC,]
temp <- datInterior[,c("MeanPlotSiteIndex",..vars)]
#temp <- datCoast[,c("MeanPlotSiteIndex",..vars)]

rf <- randomForest(MeanPlotSiteIndex ~ ., data = temp, importance = T, proximity = T)
imp <- importance(rf)
treeClm[,eq1 := 2.801+0.0616*DD5-0.0202*DD_18-0.1536*Eref]
# treeClm[,eq2 := DD5*0.022]
# plot(MeanPlotSiteIndex ~ eq1, data = treeClm)
# 

modInt <- step(lm(MeanPlotSiteIndex ~1, data = dat), 
     scope = list(lower = ~1, upper = ~ DD5*DD_18*Eref*CMD*PAS_wt), trace = 3)
summary(modInt)
plot(datInterior$MeanPlotSiteIndex,modInt$fitted.values)

modCoast <- step(lm(MeanPlotSiteIndex ~1, data = datCoast), 
     scope = list(lower = ~1, upper = ~ DD5*DD_18*Eref*CMD*PAS_wt), trace = 3)
summary(modCoast)
plot(datCoast$MeanPlotSiteIndex,modCoast$fitted.values)



modAll <- step(lm(MeanPlotSiteIndex ~1, data = dat), 
     scope = list(lower = ~1, upper = ~ DD5*DD_18*Eref*CMD*PAS_wt), trace = 3)
summary(modAll)
plot(dat$MeanPlotSiteIndex,modAll$fitted.values)









fit2 <- lm(MeanPlotSiteIndex ~ DD5 + DD_18 + Eref + CMD + DD5:DD_18 + 
    DD5:Eref + DD_18:Eref + DD5:CMD + DD5:DD_18:Eref, data = treeClm)
plot(treeClm$MeanPlotSiteIndex,fit2$fitted.values)

fit2 <- lm(MeanPlotSiteIndex ~ DD5 + DD_18 + Eref + CMD + DD5:DD_18, data = treeClm)
plot(treeClm$MeanPlotSiteIndex,fit2$fitted.values)

coefs <- fit2$coefficients
treeClm[,eq3 := coefs[1]+coefs[2]*DD5+coefs[3]*DD_18+coefs[4]*Eref+coefs[5]*DD5*DD_18]
treeClm[,testEq := 8.492 + 0.0222*Eref]
```
Predict into US BGCs

```{r USPred}
#climUS <- fread("C:/Users/kirid/Sync/CCISS_data/CommonTables/WNA_4k_HexPts_BGC_Normal_1961_1990MSY.csv")
climUS <- climDat0[,lapply(.SD, mean), by = .(BGC), .SDcols = 174:252]
vars <- names(climUS)[-1]

climUS[grep("^C.*",BGC),PredSI := predict(modCoast, newdata = climUS[grep("^C.*",BGC),-1])]
climUS[is.na(PredSI),PredSI := predict(modInt, newdata = climUS[is.na(PredSI),-1])]
climUS$PredSI <- predict(modAll, newdata = climUS[,-1])
#climUS$BGC <- factor(climUS$BGC, levels = climUS$BGC[order(climUS$DD5)])
pred <-  climUS[,.(BGC,DD5,PredSI)]
pred <- pred[PredSI > 0,]
pred[PredSI < -5 | PredSI > 40, Lab := BGC]

ggplot(pred, aes(x = DD5, y = PredSI))+
  geom_point()+
  geom_text(aes(label = Lab), size = 3)


suit <- pred[suit, on = "BGC"]
```


```{r simple model}
sibec <- fread("./inputsGit/SIBEC_2013_Summary.csv")
Spp = "Fd"
sibec <- sibec[TreeSpp == Spp,]
sibec[,BGC := gsub("/.*","",SS_NoSpace)]
sibec[,isMax := MeanPlotSiteIndex == max(MeanPlotSiteIndex), by = .(BGC)]
sibec <- sibec[(isMax),]

#climDat <- fread("C:/Users/kirid/Sync/CCISS_data/CommonTables/WNA_4k_HexPts_BGC_Normal_1961_1990MSY.csv")
climDat0 <- fread("C:/Users/whmacken/Sync/CCISS_data/CommonTables/WNA_4k_HexPts_BGC_Normal_1961_1990MSY.csv")
climDat <- climDat0[,lapply(.SD, mean), by = .(BGC), .SDcols = 174:252]
vars <- names(climDat)[-1]
#suit <- fread("C:/Users/kirid/Sync/CCISS_data/CommonTables/Feasibility_v11_21.csv")
suit <- fread("C:/Users/whmacken/Sync/CCISS_data/CommonTables/Feasibility_v11_21.csv")
suit <- suit[Spp == "Fd",.(BGC,SS_NoSpace,Spp,Feasible)]
suit[,isMax := Feasible == min(Feasible), by = .(BGC)]
suit2 <- suit[(isMax), head(.SD,1), by = .(BGC)]
sibec <- merge(sibec, suit2, by = "BGC", all = T)
#units <- fread("C:/Users/kirid/Sync/CCISS_data/CommonTables/All_BGCs_v11_21.csv")
units <- fread("C:/Users/whmacken/Sync/CCISS_data/CommonTables/All_BGCs_v11_21.csv")
BC.units <- units[DataSet == "BC",Map_Label]
climDat <- climDat[BGC %in% BC.units,]
treeClm <- sibec[climDat, on = "BGC"]


```


```{r simple regression}
require(forcats)
require(stringr)

#allDat$ID2 <- as.character(allDat$ID2)
coastDat <- allDat %>% dplyr::filter(str_detect(ID2, ("CWH|CDF|CMX|MH|MHRF|CVG|CRF|CMA|CWF|CCH")))#, "CMX", "MH", "MHRF", "CVG", "CRF")))
interDat <- allDat %>% dplyr::filter(!str_detect(ID2, ("CWH|CDF|CMX|MH|MHRF|CVG|CRF|CMA|CWF|CCH")))#, "CMX", "MH", "MHRF", "CVG", "CRF")))
pc <- ggplot(coastDat, aes(x = fct_reorder(ID2, DD18), y = DD18))+
  geom_point() +
  #geom_point(shape = 21, fill = "red", size = 1)+
  #geom_jitter(width = 0) +
  coord_flip()+
    ggtitle("DD5 range by Coastal BGC")+
  xlab ("BGC")+
  #scale_y_continuous("DD5", breaks=seq(0,8000,500))+
  theme_bw()
  #geom_text (aes(label= BGC), size = 1, hjust = -1, position = position_dodge(width=1) )#
#ggsave("./outputs/CMD_ranges of Expert aSMR of Zonal.pdf", plot = p, dpi = "print", device = "pdf", width = 15, height = 15, units = "cm")
#ggsave("./outputs/CMD_ranges.png", plot = p, dpi = "print", device = "png", width = 15, height = 15, units = "cm")
plot(pc)

pi <- ggplot(interDat, aes(x = fct_reorder(ID2, DD18), y = DD18))+
  geom_boxplot() +
  #geom_point(shape = 21, fill = "red", size = 1)+
  #geom_jitter(width = 0) +
  coord_flip()+
    ggtitle("DD5 range by Interior BGC")+
  xlab ("BGC")+
  #scale_y_continuous("DD5", breaks=seq(0,8000,500))+
  theme_bw()
  #geom_text (aes(label= BGC), size = 1, hjust = -1, position = position_dodge(width=1) )#
#ggsave("./outputs/CMD_ranges of Expert aSMR of Zonal.pdf", plot = p, dpi = "print", device = "pdf", width = 15, height = 15, units = "cm")
#ggsave("./outputs/CMD_ranges.png", plot = p, dpi = "print", device = "png", width = 15, height = 15, units = "cm")
plot(pi)


``` 