---
title: "SiteIndex-Climate Relationship"
author: "William H MacKenzie"
date: "14/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tcltk)
require(foreach)
require(ggplot2)
require (plyr)
require(dplyr) ## this package may cause issues with count function of plyr
require(magrittr)
require(data.table)
require (reshape)
require(reshape2)
require(gridExtra)
require(mgcv)
require(rgl)
require(deldir)
require(stringr)
require(janitor)
require(modeest)
require(expss)
require(tidyr)
require (purrr)
require (purrrlyr)
require (fitdistrplus)

```

## Introduction


```{r import tables, echo=FALSE, message = FALSE}
allDat <- fread("D:/CommonTables/Climate_Data/ALLWNAv11_AllVars.csv", data.table = FALSE, stringsAsFactors = FALSE) ###Climate data 1961-90for representative points per BGC  with all variables
allDat <- allDat[!(allDat$DD5 == -9999),]
allDat <- allDat %>% dplyr::rename(., ID2 = BGC) 
CMDtemp <- allDat[,grep("CMD",colnames(allDat))]
AllBGC <- unique(allDat$ID2)
allDat$ID2 <- as.factor(allDat$ID2)
allDat <- droplevels(allDat)
#write.csv(AllBGC, "./inputs/AllmodelledBGCs.csv")
# ###work on checking for excess summer precip in all month leading to Moist aSMR zonal sites
#temp2 <- allDat[,grep("PPT0", colnames(allDat))]
sPPTtemp <- allDat[c("ID1", "ID2", "PPT05","PPT06","PPT07","PPT08","PPT09" )]
sPPTtemp$Moist <- rowSums(sPPTtemp[,3:7] >90) #count of months with >90mm rain
temp3 <- sPPTtemp %>% dplyr::select(ID2,Moist) %>% group_by (ID2) %>% summarize (count= length(ID2), moistcount = length(ID2[Moist == 5]), ratio = moistcount/count)# %>% # %>% moistcount = nrow (ID2 [temp2$ID2 == 5])#filter(Moist == 5) %>% count(ID2, sort =TRUE) %>% 
#table(temp3)
sPPTtemp$Moist <- ifelse(sPPTtemp$Moist > 4, 1, 0) # flag locations where all months are >90mm rain. If all months then always overcapacity zonal soils
                     # ifelse(temp2$Moist >3, 5.5,""))
sPPTtemp <- sPPTtemp[c("ID1","ID2","Moist")]
#temp2$Moist <- as.integer(temp2$Moist) %>% replace_na(0)

#temp2 <- temp2[temp2$Moist != "",] # only those points calculated to be moist
#####################################
wPPTtemp <- allDat[,c("ID2","PPT_at","PPT_wt","PAS")]
allDat2 <- cbind(wPPTtemp,CMDtemp)
#allDat <- cbind(wPPTtemp,sPPTtemp[c("Moist")])
#allDat <- cbind(allDat,temp,temp2) ### use this one if Moist indicator is completed above
allDat2$PPT.dorm <- allDat2$PPT_at + allDat2$PPT_wt
 CMD <- aggregate( . ~ ID2, allDat2, mean) ##
# Moist <- aggregate(ID1 ~ ID2 + Moist, temp2, length) # count of number of sites in each BGC meeting moist criteria

# ##--------BGCs requiring special adjustments for deep snowpack
    BGC_Special <- fread("./inputsGit/BGC_Special.csv", data.table = FALSE)
    CMD <- full_join(CMD,BGC_Special, by.x = "ID2")

  ####To adjust in zones with prolonged snowpack remove CMD from early growing season months
    CMD$CMDsnow <- ifelse(CMD$Special == "snow", CMD$CMD07+CMD$CMD08+CMD$CMD09,
                   CMD$CMD02+CMD$CMD03+CMD$CMD04+CMD$CMD05+CMD$CMD06+CMD$CMD07+CMD$CMD08+CMD$CMD09)
    CMD$CMD <- CMD$CMDsnow
##-----Start of Growing season deficits 
###adds deficit from incomplete recharge in dormant season. Estimated holding capcity of loamy soils is approximately 350mm.
## 500m seems to be a better fit - approximates the extreme years
CMD <- CMD[,c("ID2","CMD","PPT.dorm")]
CMD$Def <- 500 - CMD$PPT.dorm 
#----------------------temporary adjustment of CMD based on vegetation analysis
  # Adjust <- fread("CMD_adjustments.csv", data.table=getOption("datatable.fread.datatable", TRUE))## 
  # CMD <- merge(CMD,Adjust, by.x = "ID2")
  # CMD$CMD <- CMD$CMD + CMD$CMD_Adjust
#----------------------
CMD$Def[CMD$Def < 0] <- 0 #negative values set to zero = no deficit
CMD$CMD <- CMD$CMD + CMD$Def
CMD <- CMD[,c("ID2","CMD")] # CMD now equals CMD.total

###for each wetter rSMR, previous CMD is divided by 2
for (i in 1:3){
  CMD[,2+i] <- CMD[,1+i]/2
}
colnames(CMD) <- c("BGC","rSMR4","rSMR5","rSMR6","rSMR7")
CMD <- CMD[,c(1,3:5,2)]

###for each drier rSMR, previous CMD + 100
for (i in 1:4){
  CMD[,length(CMD)+1] <- CMD[,length(CMD)] + 125
}
colnames(CMD)[6:9] <- c("rSMR3","rSMR2","rSMR1","rSMR0")

CMD <- CMD[,order(colnames(CMD))]## creates full grid of CMD values by BGC by rSMR class
write.csv (CMD, "./outputs/CMD_by_rSMR.csv")
```
## Range of Climatic Moisture Deficit for Expert Assigned aSMR Class  of Zonal Sites
The development of a seamless climate surface for British Columnbia with Climatic Moisture Deficit presented an opportunity for linking aSMR as defined by AET/PET ratio to the climate moisture deficit. Since the zonal site is thought to best reflect climatic conditions a comparison of the CMD range reprenting each of the aSMR classes as defined in the 1990 expert grid was used to define some initial CMD ranges that represent each class. Errors in aSMR assignment and in the Climate Surface are both likley but in aggregate believed to be generally accurate.
### Boxplot of CMD ranges by expert rSMR4 class for creation of initial CMD ranges and ID of BGC outliers. A aSMR class of '5' = FRESH

```{r box plot of climate variable by BGC, echo=FALSE, message = FALSE, fig.width=11,fig.height=50,fig.cap="\\label{fig:figs} Climate values by BGC"}
require(forcats)
require(stringr)

#allDat$ID2 <- as.character(allDat$ID2)
coastDat <- allDat %>% dplyr::filter(str_detect(ID2, ("CWH|CDF|CMX|MH|MHRF|CVG|CRF|CMA|CWF|CCH")))#, "CMX", "MH", "MHRF", "CVG", "CRF")))
interDat <- allDat %>% dplyr::filter(!str_detect(ID2, ("CWH|CDF|CMX|MH|MHRF|CVG|CRF|CMA|CWF|CCH"))) %>% dplyr::filter(!(ID2 == "MSSD"))#, "CMX", "MH", "MHRF", "CVG", "CRF")))

pc <- ggplot(coastDat, aes(x = fct_reorder(ID2, DD5), y = DD5))+
  geom_boxplot() +
  #geom_point(shape = 21, fill = "red", size = 1)+
  #geom_jitter(width = 0) +
  coord_flip()+
    ggtitle("DD5 range by Coastal BGC")+
  xlab ("BGC")+
  #vline()+
  #xlim (150, 200) +
  theme_bw()
  #geom_text (aes(label= BGC), size = 1, hjust = -1, position = position_dodge(width=1) )#
#ggsave("./outputs/CMD_ranges of Expert aSMR of Zonal.pdf", plot = p, dpi = "print", device = "pdf", width = 15, height = 15, units = "cm")
#ggsave("./outputs/CMD_ranges.png", plot = p, dpi = "print", device = "png", width = 15, height = 15, units = "cm")
plot(pc)

pi <- ggplot(interDat, aes(x = fct_reorder(ID2, DD5), y = DD5))+
  geom_boxplot() +
  #geom_point(shape = 21, fill = "red", size = 1)+
  #geom_jitter(width = 0) +
  # ylim(0, 2500)+ 
  coord_flip()+
    ggtitle("DD5 range by Interior BGC")+
  xlab ("BGC")+
     theme_bw()
  #geom_text (aes(label= BGC), size = 1, hjust = -1, position = position_dodge(width=1) )#
#ggsave("./outputs/CMD_ranges of Expert aSMR of Zonal.pdf", plot = p, dpi = "print", device = "pdf", width = 15, height = 15, units = "cm")
#ggsave("./outputs/CMD_ranges.png", plot = p, dpi = "print", device = "png", width = 15, height = 15, units = "cm")
plot(pi)


``` 


```{r simple regression}
require(forcats)
require(stringr)

#allDat$ID2 <- as.character(allDat$ID2)
coastDat <- allDat %>% dplyr::filter(str_detect(ID2, ("CWH|CDF|CMX|MH|MHRF|CVG|CRF|CMA|CWF|CCH")))#, "CMX", "MH", "MHRF", "CVG", "CRF")))
interDat <- allDat %>% dplyr::filter(!str_detect(ID2, ("CWH|CDF|CMX|MH|MHRF|CVG|CRF|CMA|CWF|CCH")))#, "CMX", "MH", "MHRF", "CVG", "CRF")))
pc <- ggplot(coastDat, aes(x = fct_reorder(ID2, DD5), y = DD5))+
  geom_boxplot() +
  #geom_point(shape = 21, fill = "red", size = 1)+
  #geom_jitter(width = 0) +
  coord_flip()+
    ggtitle("DD5 range by Coastal BGC")+
  xlab ("BGC")+
  #scale_y_continuous("DD5", breaks=seq(0,8000,500))+
  theme_bw()
  #geom_text (aes(label= BGC), size = 1, hjust = -1, position = position_dodge(width=1) )#
#ggsave("./outputs/CMD_ranges of Expert aSMR of Zonal.pdf", plot = p, dpi = "print", device = "pdf", width = 15, height = 15, units = "cm")
#ggsave("./outputs/CMD_ranges.png", plot = p, dpi = "print", device = "png", width = 15, height = 15, units = "cm")
plot(pc)

pi <- ggplot(interDat, aes(x = fct_reorder(ID2, DD5), y = DD18))+
  geom_boxplot() +
  #geom_point(shape = 21, fill = "red", size = 1)+
  #geom_jitter(width = 0) +
  coord_flip()+
    ggtitle("DD5 range by Interior BGC")+
  xlab ("BGC")+
  #scale_y_continuous("DD5", breaks=seq(0,8000,500))+
  theme_bw()
  #geom_text (aes(label= BGC), size = 1, hjust = -1, position = position_dodge(width=1) )#
#ggsave("./outputs/CMD_ranges of Expert aSMR of Zonal.pdf", plot = p, dpi = "print", device = "pdf", width = 15, height = 15, units = "cm")
#ggsave("./outputs/CMD_ranges.png", plot = p, dpi = "print", device = "png", width = 15, height = 15, units = "cm")
plot(pi)


``` 